Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls

### 2024-11-05 paper/paper.qmd
test

>>>>

This study employs various R packages (@R) for data cleaning and analysis, including libraries from tidyverse (@tidyverse), ggplot2 (@ggplot2), rstanarm (@rstanarm), testthat (@Test), here (@Here), janitor (@janitor), lubridate (@lubridate), broom (@broom), dplyr (@dplyr), knitr (@knitr), and modelsummary (@ModelSummary). Lastly, the arrow was used to store data efficiently.
